Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students: A replication analysis using data from the United States and a case study on the Netherlands

### 2024-02-14 paper/paper.qmd
Made edits to the Data & results section

(3) School closures contributed significantly to the decline in students' pass rates in mathematics and ELA in the 2020-2021 school year. Changes in ELA scores were smaller than mathematics scores, but significantly larger in districts with larger populations of students who are Black, Hispanic, English Language Learners (ELL) or eligible for free and reduced price lunch (FRPL).

@@

This dataset is obtained from the Oxford COVID-19 Policy Tracker, a project that collected information on COVID-19 policy measures for the years 2020, 2021 and 2022 [@Hale]. For 185 countries, the dataset assigns a daily Tracker score for each day between January 1st, 2020, and December 31st, 2022. Note that a Tracker score is defined as an integer value between 0 and 3, with a value of 2 or 3 denoting a school closure [@Jack_Oster_2023].

@@

This dataset is a csv version of `scores_lm_demographics.dta` obtained from the final dataset found in the data repository for “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@TestScore]. This dataset contains extensive information on various school districts across the aforementioned 11 states, including information on the shares of students by race, the share of schooling done in-person, and changes in average test scores in both Math and ELA from the previous year across the years 2018-2019 and 2021-2022 (no information is present regarding the year 2020 as all standardised assessments were cancelled due to the pandemic).

@@

@fig-daysclosed depicts the average number of school closures by region, as defined by the World Bank, between the start of January 2020 and the end of December 2021. In particular, it employs data on 185 countries, each of which is assigned its particular region, and provides the average number of school closures for nations in each region between the aforementioned time frame.

In order to achieve this, we first created the dataset `country_region.csv` which assigns each of the 185 countries present in the primary dataset, `region_data.csv`, its respective region. This was done since `region_data.csv` did not feature each nation's region, and as such, by creating the `country_region.csv` dataset we were able to 'merge' the two sets of information so that the final product featured all information regarding the Covid Tracker score of each country one each day, as well as the region the country is in.

We initially cleaned the data in `region_data.csv` by omitting information from the year 2022 in a bid to replicate and examine the internal validity of the work by Jack and Oster who also omitted the year 2022 from their figure [@Jack_Oster_2023]. From there, only the columns of interest were kept which detailed the country name, (empty) region name, date, and Covid Tracker score. We also found a minor spelling error of the Faroe Islands which were incorrectly spelled as Faeroe Islands which we also amended in the cleaning process. From here, we simply merged the cleaned `region_data.csv` with the regions listed in `country_region.csv` in order fill in the empty region names present in the original dataset.

With the cleaned dataset, we were able to create the figure detailing the average days closed by region by first grouping the cleaned data by region name and country, then summing the number of instances where a Tracker score of 2 or 3 was present (as this defines a school closure as per Jack and Oster's work [@Jack_Oster_2023]). From there, we calculated the mean number of days closed by region by computing the average number of days closed for all nations in a given region.

Then, in an attempt to garner a deeper understanding of how the US compares to other nations with regards to their COVID-19 schooling policies and measures, we employ @tbl-daysclosed which provides a snippet of the top 5 countries by number of school closures between the start of January 2020 and the end of December 2021. Due to the US featuring the second-highest number of school closures, @tbl-daysclosed specifically depicts the top 5 nations in an attempt to evidence the US’ large number of closures relative to the rest of the world. In order to generate this figure, we employed the same cleaned dataset used to create @fig-daysclosed. In this particular case, we simply grouped the data by country and summed the number of instances where a country registered a Covid Tracker score of 2 or 3 and reported a snippet of the generated table detailing each country and the number of school closures it faced in the aforementioned time frame.

@@

The purpose of Figures \ref{fig-broadband} and \ref{fig-race} is to explore the correlations between certain district and county characteristics, and the average number of virtual school days for the respective district or county. Specifically, we look at broandband usage by county, and the shares of four races (White, Black, Asian, Hispanic) by district. For each county or district, we assign "high" or "low" depending on if their level for the characteristics being explored is above or below their state's median, respectively. By doing so, we allow for the results to be driven by a variation within states, as opposed to variation across states.

We start by using `nces_district_enrollment_2018_2020.csv.zip`. As previously mentioned, this data set splits the total enrollment into various categories. We start by converting the columns into the numeric class as appropriate. Some enrollment cells did not have a value, indicating that data was not collected for that specific metric. These occurred a handful of times for certain races within certain districts. These NAs were replaced with 0s. For our paper, we are concerned specifically with race. Thus, for each district, we calculate the total number of White, Black, Asian, and Hispanic students enrolled. Given the structure of the data, this is done by summing the total enrollment per race for Male and Female for each district. Next the total enrollment for the whole district was calculated, before then calculating the share of total enrollment that each race comprises.

The data above was then separated into different tables for each race. For each race, we then classified the district as either "High" or "Low" depending on if their share was above or below their respective state's median. Using this data, we were now interested in the number of virtual days that each of these districts had. This information was available in the `District_Overall_Shares.csv` data set. Given that the US average number of school days per year is 180, the percentage for share_virtual was multiplied by 180 for each district.

Next, the aforementioned data for each race that separated the districts into quantiles, and the data for the number of virtual days per district were merged. This results in some NAs being produced since the data set on race had more districts than the data on the number of virtual days. Given the lack of data, all NAs were droppped. Finally, the number of virtual days for the "High" quantile and the "Low" quantile were averaged. This results in four data sets, one for each race considered.

To calculate the information regarding broadband, we started with the `broadband_data_2020October.csv` data set. Only columns that were necessary were kept, and the columns were converted to the numeric class as appropriate. Each county was then classified as either "High" or "Low" depending on if their share was above or below their respective state's median. A single county contains multiple districts, and since our data regarding the number of virtual days was based on district, the data was averaged across districts for each county. `nces_district_directory_2018.dta` provided information on which county each district belonged to, and was merged with the previous data that calculated the average number of virtual days for each district, before then calculating the average number of virtual days for each county. Finally, we average the number of virtual days for the counties labelled "High" and "Low."

@@

# Results
Data from the Oxford COVID-19 Policy Tracker [@Hale] and World Bank [@worldbank2023] were used to determine the average number of school closures by regions worldwide between January 2020-December 2021. We reconstruct this result in Figure \ref{fig-daysclosed} and extract the top 5 countries with the highest average number of closures in Table \ref{tbl-daysclosed}. Figure \ref{fig-daysclosed} shows that North America had the highest at 535 days, which is around 73% of the two-year period, whilst sub-Saharan Africa had the least at 300 days, or around 38% of the two-year period. Thus, countries with the longest closures spent more than twice the amount of time in virtual schooling compared to those with the shortest closures.

@@

@@

Moreover, data from CSDH [@citeraw1], NCES [@citeraw2] and Microsoft [@kahan2020usbroadband] were used to delve deeper and analyse correlations between the average number of virtual schools days, and certain demographic characteristics, and Figures \ref{fig-broadband} and \ref{fig-race} were created. As discussed previously, Figure \ref{fig-broadband} shows the average number of virtual days for counties that were classified as "Low" and those classified as "High," whilst Figure \ref{fig-race} shows the average for districts. The classification of districts and counties was explained in @sec-datacleaning2.

We built upon the research done by Jack and Oster [-@Jack_Oster_2023] in their paper by firstly utilising a different methodology. Jack and Oster had weighted their results by total district enrollment, thus, districts with larger enrollments will have a greater impact on the overall average than districts with smaller enrollments. In our paper, we do not weight it by enrollment, which allowed us to treat each district equally, regardless of its size. This offers a more balanced view of the educational landscape without overemphasising larger districts. We also enriched the analysis on the average virtual days by race by also considering the shares of White and Asian students, with the goal of better analysing the nuanced impact of racial demographics. Moreover, it is important to note that Jack and Oster did not mention their methodololgy for finding the virtual days for each county, given that data was only available for district. As previously mentioned, we found this metric by averaging across the districts found in each county.

@@

Figure \ref{fig-broadband} shows that the average number of virtual days for counties that were on the lower end of broadband usage for their respective states was 20 days, whilst the average number of virtual days for the "High" counties was 24 days. This result is quite different from the one obtained by Jack and Oster [-@Jack_Oster_2023], whereby they found that the average for "Low" counties was 55 days, and "High" counties was 48 days. Thus, not only are the number of days for the quantitles different, but our analysis found that the counties with lower broadband had less virtual days. The discrepancy in data can arise due to numerous reasons. Firstly, we did not weight the data by enrollment. Secondly, we neglected the cells without any data, whereas Jack and Oster may have dealt with these in a different manner. Lastly, their method of finding average virtual days for a county may be different. The observed differences in virtual learning days between counties with varying broadband usage levels highlight potential disparities in access to and the usage of online education resources. This suggests that regions with lower broadband usage may face additional challenges in facilitating effective virtual learning experiences for students.

@@

Finally, data from ... was used to examine changes in district-level pass rate data from 11 state standardised assessments, taken in the spring of 2018, 2019 and 2021. We again reconstruct and extend the data...

```{r}
#| label: fig-mathscoresbyonline
#| echo: false
#| message: false
#| warning: false 
#| fig-cap: "Test score by percent online (change)"

@@

@@

```{r}
#| label: fig-testscoresela
#| echo: false
#| message: false
#| fig-cap: "Update"
# Filter for Math
filtered_test_data <- cleaned_test_score_data |>
  filter(subject == "ELA")

@@

(1) Between January 2020 and December 2021, the United States experienced the second-highest number of days of school closed worldwide, with an average of 667 days. In fact, it falls second only to Azerjiban, which recorded an average of 669 days.
(2) Access to in-person education was unequal by demographic characteristics. More disadvantaged districts, *i.e.*, those with higher proportions of racial minorities and lower broadband usage spent more days in virtual schooling.
(3) During the 2020-2021 school year, students' pass rates on standardised assessments declined by 12.8 percentage points in mathematics and 6.8 in ELA. Declines were more severe in more disadvantaged districts, *i.e.*, those with higher proportions of racial minorities, ELL and FRPL students.

@@

Moreover, stratifying test assessment scores by district-level race, ELL and FRPL shares may be problematic. The underperformance of vulnerable populations in relation to more privileged populations may reinforce discriminatory notions about their intellectual ability. These notions are harmful, having been found to impair even further the academic performance of minority groups [@steele]. Indeed, Steele and Aronson [-@steele] have found that, when an individual is conscious of the negative stereotypes of their group, they face *stereotype threat*, becoming fearful of confirming or being judged by those stereotypes through their actions or performance. This may lead to increased self-doubt and anxiety, and thus poorer performance on assessments.

@@

What is more, Jack et al.'s [-@Jack2] standardised assessments data excludes information about the corresponding broadband usage and unemployment rates by district. It instead includes data of the corresponding shares of ELL and FRPL students by district. This discrepancy prevents us from telling a full story as to how the pass rates of schools located in districts with lower broadband usage and employment rates, known to face more days of school closed than the national average, were affected. We also question whether the shares of FRPL students are a good estimator of the shares of students with low socioeconomic status. Though FRPL enrollment are widely used in education research as an indicator of student poverty, there is emerging literature that it serves as a poor proxy for poverty [@Fazlul2023]. In fact, using multiple data sources external to the American school system, Fazlul et al. [-@Fazlul2023] show that FRPL rates greatly exceed what would be expected from stated income thresholds for program participation by 35 to 50%. This suggests that the shares of FRPL students per district may not be the most optimal estimator of student poverty, and that more insightful conclusions could have been obtained in examining instead, for instance, the shares of students in low-income households per district.

>>>>

(3) School closures contributed significantly to the decline in students' pass rates in mathematics and ELA in the 2020-2021 school year. Changes in ELA scores were smaller than mathematics scores, but significantly larger in districts with larger populations of students who are Black or Hispanic.

@@

This dataset is made available by the Oxford COVID-19 Policy Tracker, a project that collected information on COVID-19 policy measures in 185 countries for the years 2020, 2021 and 2022 [@Hale]. Data were collected by a team of over 1500 volunteers at Oxford's Blavatnik School of Government from publicly available sources-- such as government press releases, briefings, international organisation reports, and credible news articles. For 185 countries, this dataset assigns a daily Tracker score between January 1st, 2020, and December 31st, 2022. This daily Tracker score is a composite integer measure of nine response metrics that evaluate the stringency of a country's COVID-19 response [@Hale]; in particular, a value of 2 or 3 denotes a school closure [@Jack_Oster_2023].

@@

This dataset is a `.csv` version of `scores_lm_demographics.dta`, obtained from the replication package of “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@Jack_Oster_2], published in the American Economic Association’s *AER: Insights* [@citeAEA]. Data are obtained from the Departments of Education of the aforementioned 11 US states, each of whom collect data from constituent schools, school boards and school authorities [@DeptsEd]. The dataset contains extensive information on school districts across these 11 states, including shares of students by race, shares of schooling done in-person, and changes in average test scores in both Mathematics and ELA from the previous year across the years 2018-2019 and 2021-2022. Note no information on test scores are available for 2020, as all standardised assessments were cancelled due to the pandemic.

@@

@fig-daysclosed shows the average number of school closures by region between the start of January 2020 and the end of December 2021. The Oxford COVID-19 Policy Tracker [@Hale] assigns a score to each of the 185 countries and the World Bank [@worldbank2023] provides a one-to-one correspondence between the country and the broader region to which it belongs: sub-Saharan Africa, Europe and Central Asia, and so forth. Details on how this figure was achieved follow.

Since `region_data.csv` did not feature the region to which each of the 185 countries belonged, we created the dataset `country_region.csv`. This assigned to each country its corresponding region, as defined by the World Bank [@worldbank2023].  In doing so, we could have information both on the COVID-19 Tracker score of each country for each day, as well as the region in which the country is located.

We followed the workflow of Jack and Oster [@Jack_Oster_2023], by likewise omitting in `regions.csv` all information from the year 2022. Only columns of interest to the analysis were then kept, including the country name, (empty) region name, date, and COVID-19 Tracker score. We also identified and amended a minor spelling error in the name of `Faroe Islands`, originally misspelled as `Faeroe Islands`. Thereafter, we merged the cleaned `region_data.csv` with the regions listed in `country_region.csv` in order fill in the empty region names present in the original dataset.

We regrouped the cleaned data by region name and country, summed the number of instances where a Tracker score of 2 or 3 was present (as this defines a school closure, as per Jack and Oster [-@Jack_Oster_2023]). We then calculated the mean number of days closed by region by computing the average number of days closed for all countries in a given region.

To gain an understanding of how COVID-19 schooling measures implemented in the United States compared with those elsewhere in the world, we created @tbl-daysclosed. This table provides a snippet of the top 5 countries with the highest number of school closures in 2020-2021, featuring the US in second place. We used the same cleaned dataset as before, regrouped data by country, summed the number of instances where a country registered a COVID-19 Tracker score of 2 or 3 and isolated the top 5 countries where these numbers were the largest.

@@

Figures \ref{fig-broadband} and \ref{fig-race} explore correlations between the average number of school closures with two county- and district-level characteristics, these being county-level broadband usage and district-level race shares of four major ethnic classes-- White, Black, Asian and Hispanic. For both demographic characteristics, we followed Jack and Oster's [-@Jack_Oster_2023] work, by assigning to each county or district a quantile of "High" or "Low", depending on whether its levels for said characteristic were above or below the state's median, respectively. By doing so, we allowed the results to be driven by a variation within states, as opposed to variation across states.

We drew on the `nces_district_enrollment_2018_2020.csv.zip` dataset, which reports the total student enrollment by grade, sex and ethnic class. A handful of enrollment cells had no value, which were subsequently replaced by 0s. Being specifically concerned with race data, we calculated for each district the total number of White, Black, Asian, and Hispanic students enrolled. We then separated data according to race, classifying districts as "High" or "Low", depending on whether their race share was above or below their state's median. Thereafter, we matched each district with those contained in `District_Overall_Shares.csv`, so as to obtain information on its average number of days closed. We found there was some discrepancy, with the number of districts in `nces_district_enrollment_2018_2020.csv.zip` being larger than that in `District_Overall_Shares.csv`, which we resolved by dropping all instances of districts not present in both datasets. After merging these two datasets, we averaged the number of virtual days across districts, classified in the "High" and "Low" quantiles. This resulted in four data sets, one for each race considered.

Here, we differed from the methodology employed by Jack and Oster [-@Jack_Oster_2023] in one specific way. In their workflow, Jack and Oster [-@Jack_Oster_2023] also weighted the average number of days of virtual school by total district enrollment. In this way, districts with larger enrollments had greater impact on the overall average than those with smaller enrollments. In our analysis, we omitted such weighting, instead treating each district equally, regardless of size. This offered a more balanced view of the educational landscape, without overemphasising larger districts.

To address broadband usage, we drew on `broadband_data_2020October.csv` and `nces_district_directory_2018.dta`. With the former, we obtained the broadband usage across all US districts; with the latter, we regrouped all districts belonging to each US county and averaged their broadband usages. We then assigned to each county a quantile of "High" or "Low", according to whether their broadband usage was above or below their respective state's median. As before, we used `District_Overall_Shares.csv` to determine the average number of days in virtual schooling for all counties labelled as "High" and "Low."

@@

@fig-mathscoresbyonline and @fig-elascoresbyonline explore the relationship between the share of in-person learning and change in test scores in standardised tests in Mathematics and ELA respectively. In particular, they examine changes in test scores across 3 years (2021, 2019, and 2018) from the year prior (excepting the case of 2021, where changes are relative to 2019).

To achieve this, we made use of the `scores_lm_demographics.dta` dataset. However, we first converted the dataset into a `.csv` file, `scores_lm_demographics.csv`, to be used in the cleaning and analysis processes. From there, we cleaned the data by only selecting the columns of interest, those being the share of in-person learning, the subject of the test, the changes across each of the three years of interest, the number of students enrolled in each school district, and the shares of each of the three races of interest (White, Black, Asian and Hispanic). To generate the aforementioned figures, we first calculated the total number of students enrolled across all school districts. We then filtered by subject, so as to deal with one subject at a time when creating the two figures. We proceeded by defining four in-person categories of 0-25%, 25-50%, 50-75%, and 75-100%, after which we mutated our filtered data by assigning each school district one of the four categories. We then proceeded to group the data by year (one of the three previously mentioned), and by in-person category so that we were able to calculated the weighted average change in test scores for each in-person category in each year. Finally, we ungrouped the data to calculate the overall, and thus un-weighted, average change in test scores for each of the three years. This was repeated for both Mathematics and ELA test scores by simply changing the filtering of the data to only include one of the two.

@fig-mathscoresrace, @fig-elascoresrace examine these test score changes from a different lens. Instead of considering the share of in-person learning, it explores the possibility of a systematic difference in the changes in test scores based on the relative share of various races. In particular, the figures examine the correlation between changes in test scores and the relative quantile share of White, Black, and Hispanic students which is one of "Low", "Middle" or "High". As before, this is also done for each of the three years of interest for each of the three races.

To generate this graph, we once again employed the cleaned `scores_lm_demographics.csv` file as was used to generate @fig-mathscoresbyonline and @fig-elascoresbyonline. We first filtered by subject to only consider one at a time, after which the total enrollment across all school districts was calculated as well as the three quantiles, "Low", "Middle", and "High", for each of the three races. From there, we grouped the data by year and quantile for each of the three races, then calculated the weighted average change in test scores for each subject and quantile, across all races and years. From there, we simply combined the summary statistics for each of the races and their respective quantiles, and showcased them in the figures, differentiating by race through shape, and year through color.

# Results

## Extent of School Closures in the United States and the World

@@

Data from the Oxford COVID-19 Policy Tracker [@Hale] and World Bank [@worldbank2023] were used to determine the average number of school closures by regions worldwide between January 2020-December 2021. We reconstruct this result in Figure \ref{fig-daysclosed} and extract the top 5 countries with the highest average number of closures in Table \ref{tbl-daysclosed}. Figure \ref{fig-daysclosed} shows that North America had the highest at 535 days, which is around 73% of the two-year period, whilst sub-Saharan Africa had the least at 300 days, or around 38% of the two-year period. Thus, countries with the longest closures spent more than twice the amount of time in virtual schooling compared to those with the shortest closures.

@@

## Average Number of School Closures by Local Demographic Characteristics

Data from CSDH [@citeraw1], NCES [@citeraw2] and Microsoft [@kahan2020usbroadband] were used to determine correlations between the average number of virtual schools days, and certain demographic characteristics. We reconstruct these results in Figures \ref{fig-broadband} and  \ref{fig-race}. These show the average number of virtual days for counties or districts that have "High" or "Low" levels of broadband usage and various race shares, respectively. Note that we enriched Jack and Oster's [-@Jack_Oster_2023] analysis on race by also considering the shares of White and Asian students, so as to better understand the nuanced impact of racial demographics. Moreover, it is important to note that Jack and Oster did not mention their methodololgy for finding the virtual days for each county, given that data was only available for district. As previously mentioned, we found this metric by averaging across the districts found in each county.

@@

Figure \ref{fig-broadband} shows that the average number of virtual days for counties that were on the lower end of broadband usage for their respective states was 20 days, whilst the average number of virtual days for the "High" counties was 24 days. This result is quite different from the one obtained by Jack and Oster [-@Jack_Oster_2023], whereby they found that the average for "Low" counties was 55 days, and "High" counties was 48 days. Thus, not only are the number of days for the quantiles different, but our analysis found that the counties with lower broadband had less virtual days. The discrepancy in data can arise due to numerous reasons. Firstly, we did not weight the data by enrollment. Secondly, we neglected the cells without any data, whereas Jack and Oster may have dealt with these in a different manner. Lastly, their method of finding average virtual days for a county may be different. The observed differences in virtual learning days between counties with varying broadband usage levels highlight potential disparities in access to and the usage of online education resources. This suggests that regions with lower broadband usage may face additional challenges in facilitating effective virtual learning experiences for students.

@@

## Standardised Test Assessment Scores

```{r}
#| label: fig-mathscoresbyonline
#| echo: false
#| message: false
#| warning: false 
#| fig-cap: "Test score by percent online (change)"
#| fig-pos: H

@@

Finally, data from “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@TestScore] was used to examine changes in district-level pass rate data from 11 state standardised assessments, taken in the spring of 2018, 2019 and 2021.

@@

```{r}
#| label: fig-elascoresrace
#| echo: false
#| message: false
#| fig-cap: "Update"
# Filter for Math
filtered_test_data <- cleaned_test_score_data |>
  filter(subject == "ELA")

@@

(1) Between January 2020 and December 2021, the United States experienced the second-highest number of days of school closed worldwide, with an average of 667 days. In fact, it falls second only to Azerjiban, which recorded an average of 669 days.
(2) Access to in-person education was unequal by demographic characteristics. More disadvantaged districts, *i.e.*, those with higher proportions of racial minorities and lower broadband usage spent more days in virtual schooling.
(3) During the 2020-2021 school year, students' pass rates on standardised assessments declined by 12.8 percentage points in mathematics and 6.8 in ELA. Declines were more severe in more disadvantaged districts, *i.e.*, those with higher proportions of racial minorities.

@@

Moreover, stratifying test assessment scores by district-level race may be problematic. The underperformance of vulnerable populations in relation to more privileged populations may reinforce discriminatory notions about their intellectual ability. These notions are harmful, having been found to impair even further the academic performance of minority groups [@steele]. Indeed, Steele and Aronson [-@steele] have found that, when an individual is conscious of the negative stereotypes of their group, they face *stereotype threat*, becoming fearful of confirming or being judged by those stereotypes through their actions or performance. This may lead to increased self-doubt and anxiety, and thus poorer performance on assessments.

@@

What is more, Jack et al. [-@Jack_Oster_2] standardised assessments data excludes information about the corresponding broadband usage and test scores of Asians by district. It instead includes data of the corresponding shares of ELL and FRPL students by district, two demographic characteristics we did not consider in our analysis. This discrepancy prevents us from telling a full story as to how the pass rates of schools located in districts with lower broadband usage and higher shares of Asian minorities, the former of which is known to face more days of school closed than the national average, were affected. We raise a question of whether the shares of FRPL students were a good estimator of the shares of students with low socioeconomic status. Though FRPL enrollment are widely used in education research as an indicator of student poverty, there is emerging literature that it serves as a poor proxy for poverty [@Fazlul2023]. In fact, using multiple data sources external to the American school system, Fazlul et al. [-@Fazlul2023] show that FRPL rates greatly exceed what would be expected from stated income thresholds for program participation by 35 to 50%. This suggests that the shares of FRPL students per district may not be the most optimal estimator of student poverty in the Jack et al. [-@Jack_Oster_2] paper, and that more insightful conclusions could have been obtained in examining instead, for instance, the shares of students in low-income households per district.
